---
title: "`r Sys.Date()`"
author: "Youen Vermard"
date: "2024-04-15"
output: html_document
---

```{r specific_options, include = FALSE, cache = FALSE, echo = FALSE, warning = FALSE, message=FALSE, progress = FALSE, verbose = FALSE}

#options(knitr.table.format = "latex")

knitr::opts_chunk$set(echo = FALSE, fig.cap = TRUE)
library(officedown)
library(officer)
library(flextable)
#library(ggalt)
library(patchwork)
library(ggrepel)
library(tidyr)
library(scales)
library(DT)


fp <- fp_par(
  text.align = "center", 
  padding.bottom = 20, padding.top = 120, 
  border.bottom = fp_border())

ft <- fp_text(shading.color='#EFEFEF', bold = TRUE)


#library(captioner)

### initialise les fonctions pour légender tables et figures
#tabcap <- captioner(prefix = "Table")
#figcap <- captioner(prefix = "Figure")

dev_chunck <- FALSE
cache_credo <- TRUE






```

<style>
body {
text-align: justify}
</style>



```{r, results='asis'}

countryList <- unique(nbreVesselTot$CLvesselFlagCountry)
  for (i in countryList){ 
    id = i
    nbreVesselInAreaTmp <- nbreVesselInArea %>% filter(CLvesselFlagCountry ==i)
    nbreVessel80PercInAreaTmp <- nbreVessel80PercInArea %>% filter(CLvesselFlagCountry ==i)
    nbreVesselInAreaVSTmp <- nbreVesselInAreaVS %>% filter(CLvesselFlagCountry ==i) %>% ungroup()
    nbreVesselFTTmp <- nbreVesselFT %>% filter(CLvesselFlagCountry ==i) %>% ungroup()
    MainSppKGTmp <- MainSppKG %>% filter(CLvesselFlagCountry ==i) %>% ungroup()
    MainSppEUROTmp <- MainSppEURO %>% filter(CLvesselFlagCountry ==i) %>% ungroup()
    
  cat("## ", i, "  \n")
  cat("In 2022, There are " ,nbreVesselInAreaTmp$nbreVessels, "active vessels" , "  \n")
  cat("Of which ",nbreVessel80PercInAreaTmp$nbreVessels,"have more than 80% of their landings in the ", Ecoregion,  "  \n")

  cat("  \n")
  cat("Vessel SIZE ", Ecoregion,  "  \n")
  
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL0006") %>% select(nbreVessels) %>% as.numeric(), "vessels are under 6m",  "  \n")
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL0608") %>% select(nbreVessels) %>% as.numeric(), "vessels are between 6 and 8m",  "  \n")
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL0810") %>% select(nbreVessels) %>% as.numeric(), "vessels are under 8 and 10m",  "  \n")
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL1012") %>% select(nbreVessels) %>% as.numeric(), "vessels are under 10 and 12m",  "  \n")
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL1215") %>% select(nbreVessels) %>% as.numeric(), "vessels are under 12 and 15m",  "  \n")
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL1518") %>% select(nbreVessels) %>% as.numeric(), "vessels are under 15 and 18m",  "  \n")
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL1824") %>% select(nbreVessels) %>% as.numeric(), "vessels are under 18 and 24m",  "  \n")
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL2440") %>% select(nbreVessels) %>% as.numeric(), "vessels are under 24 and 40m",  "  \n")
  cat(nbreVesselInAreaVSTmp %>% filter(CLvesselLengthCategory=="VL40XX") %>% select(nbreVessels) %>% as.numeric(), "vessels are over 40m",  "  \n")

  cat("  \n")
  cat("Vessel Fishing Technics ", Ecoregion,  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="DFN") %>% select(nbreVessels) %>% as.numeric(), "main activity is DFN",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="DTS") %>% select(nbreVessels) %>% as.numeric(), "main activity is DTS",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="TBB") %>% select(nbreVessels) %>% as.numeric(), "main activity is TBB",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="TM") %>% select(nbreVessels) %>% as.numeric(), "main activity is TM",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="DRB") %>% select(nbreVessels) %>% as.numeric(), "main activity is DRB",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="FPO") %>% select(nbreVessels) %>% as.numeric(), "main activity is FPO",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="HOK") %>% select(nbreVessels) %>% as.numeric(), "main activity is HOK",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="PGP") %>% select(nbreVessels) %>% as.numeric(), "main activity is PGP",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="MGO") %>% select(nbreVessels) %>% as.numeric(), "main activity is MGO",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="MGP") %>% select(nbreVessels) %>% as.numeric(), "main activity is MGP",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="PGO") %>% select(nbreVessels) %>% as.numeric(), "main activity is PGO",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="PMP") %>% select(nbreVessels) %>% as.numeric(), "main activity is PMP",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="PS") %>% select(nbreVessels) %>% as.numeric(), "main activity is PS",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="NULL") %>% select(nbreVessels) %>% as.numeric(), "main activity is NULL",  "  \n")
  cat(nbreVesselFTTmp %>% filter(CLfishingTechnique=="NO") %>% select(nbreVessels) %>% as.numeric(), "main activity is NO",  "  \n")
  
  cat("  \n")
  cat("The ten main species in tonnage in the ", Ecoregion, "are", MainSppKGTmp$CLspeciesFaoCode,  "  \n")
  cat("  \n")
  cat("The ten main species in value in the ", Ecoregion, "are", MainSppEUROTmp$CLspeciesFaoCode,  "  \n")
  
  
  cat("  \n")
  
#  nbreVesselInAreaVS_alltmp <- nbreVesselInAreaVS_all%>% filter(CLvesselFlagCountry==i)
#  tmp <- datatable(
#  nbreVesselInAreaVS_alltmp,
#  filter = "top",      # Ajoute un filtre sur chaque colonne
#  options = list(pageLength = 25)
#  )
#  print(tmp)
  
  vsTmp <- nVessel %>% 
    filter(CLvesselFlagCountry ==i) %>%
    select(CLyear, CLvesselFlagCountry, N_Vessel_Total, N_Vessel_80) %>%
    pivot_longer(
      cols = -c(CLyear, CLvesselFlagCountry),
      names_to = "variable",
      values_to = "value"
    )


print(ggplot(vsTmp, aes(x=CLyear, y=value, fill=variable)) +
    geom_bar(stat="identity") +
    labs(title=str_wrap(paste0("Number of vessels in total and having 80% of their activity in the ecoregion: ", i), width = 80), 
         x="Vessel size category", 
         y="Number of vessels") +
    theme_minimal() +
    theme(legend.position = "none"))#   cat("  \n") # <---------------------------------
}